\documentclass[margin,line]{resume}
\usepackage[colorlinks=true, pdfstartview=FitV, linkcolor=blue, citecolor=blue, urlcolor=magenta]{hyperref}
\usepackage{hyperref}
\usepackage{array}
%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Vincent Glennon}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact Information}

    \begin{tabular}{ l c l}
    E-mail: vinnyglennon@gmail.com & Address: Dublin, Ireland\\
    Phone: +353 876144261 & Skype: vinnyglennon\\
    Twitter: @vinnyglennon & Linkedin: \href{http://ie.linkedin.com/in/vinnyglennon}{vinnyglennon}\\
    Github: \href{https://github.com/vinnyglennon}{vinnyglennon} \\
    \end{tabular}

    %__________________________________________________________________________________________________________________
    % Languages
    \section{\mysidestyle Languages}

    Ruby, Php, Javascript, Java. Minor in shell scripting, Python, Perl.

    %__________________________________________________________________________________________________________________
    % Objectives
    \section{\mysidestyle Professional \\ Objectives}

    Working with like-minded people, using the best tools and technologies like agile development to \\analyse and solve real problems for users.\vspace{1mm}\\%
    Constantly acquiring new skills and improving existing ones. Rewrote \href{http://justroutes.com}{justroutes.com} from Php into Ruby(10,000 LOC into 500). Now studying \href{http://opencv.willowgarage.com/wiki/}{opencv}.\\%
    Passionate about taking great ideas and bringing them to market by the first release in a \\resource-constrained environment.\vspace{1mm}\\%
    To become a Class A programmer in terms of my peers and to specialise in performance and scalability.
    
    %__________________________________________________________________________________________________________________
    % Education

    \section{\mysidestyle Education}
    \textbf{Dublin City University}, Dublin 7, Dublin, Ireland \vspace{2mm}\\\vspace{1mm}%
    \textsl{Degree in Computer Science(Hons)} \hfill \textbf{ September 2001 -- May 2005}\\
    \textsl{Garbally College, Galway, Ireland} \hfill \textbf{September 1995 -- May 2001}\vspace{-3mm}\\\vspace{-1mm}%

    %__________________________________________________________________________________________________________________
    % Honours and Awards

    \section{\mysidestyle Honours and\\Awards} 

    Co-founded Echodio.com in San Francisco, USA. Accepted into \href{http://ycombinator.com/}{Y Combinator}, a startup incubator (2-3\% acceptance rate).\vspace{1mm}\\%
    Selected to present at South by Southwest(launchpad for Twitter.com) with Echodio in March(10\% acceptance rate).\vspace{1mm}\\%
    Shortlisted by Facebook for \href{http://useamap.}{Useamap.com} as part of their \href{http://fbfund.com/about/}{FBFund}. Been installed by 240,000 users, now defunct.\vspace{1mm}\\%
    Received coverage in majority of major Irish media outlets including 2fm, Irish Times, Sunday \\ Business Post, etc with \href{http://justroutes.com}{justroutes.com}. Selected as one of the top web applications of the year in London at FOWA with \href{http://justroutes.com}{justroutes.com}.\vspace{1mm}\\%      \vspace{1mm}\\%
    Shortlisted to the last 40, for a job in the White House(WIP), last remaining \\ computer engineer(2\% acceptance rate).\vspace{1mm}\\%
    Voted onto the Commission of Arbitration, the second highest office under the Student President by fellow Class Reps in DCU.\vspace{1mm}\\%
    Recycled unused computers from my college to a needy primacy school.\vspace{1mm}\\%

    %__________________________________________________________________________________________________________________
    % Professional Experience

    \section{\mysidestyle Professional\\Experience}

       \textbf{Betdash.com within Paddypower PLC}, Dublin, Ireland \vspace{2mm}\\\vspace{1mm}%
      \textsl{Ruby Developer} \hfill \textbf{September 2010 -- June 2011}\\
	Working within a startup style environment, mostly in backend, creating a new social sports betting game. Founders out of a startup incubator in U.S.A. \\
	Agile Development, deploying production code multiple times a day with continuous integration, unit tests, code reviews and pair programming. \vspace{1mm} \\% 
	\textsl{Skills used: Ruby 1.8.7 + 1.9.2, Rails, Blueprints, AWS, Ruby Gcc, EngineYard, web security, scaling, Redis, NewRelic, Hoptoad, PivotalTracker, Github, and everything in-between to bring a stable service live  } \vspace{1mm} \\
       \\ \textsl{Web Developer within Paddypower PLC} \hfill \textbf{July 2009 -- September 2010}\\
	Doing project estimations, system architecture and coding projects used on PaddyPower \\ Homepage(millions of users a week) or internal software for the 300+ shops. \vspace{1mm}\\%
	Agile evangelist encouraging code reviews, emergent tools usage, iterative development, \\ pair programming, refractoring code debt rather than simply patching. \vspace{1mm}\\%
    \textsl{Skills used: Php, Linux, MySql, Caching, Web Penetration Testing, server setups and Linux \\ problem solving across the team. } \vspace{1mm}\\%


    \textbf{Echodio.com}, San Francisco, USA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Co-founder} \hfill \textbf{November 2008 -- April 2009}\\
    \href{http://echodio.com}{Echodio.com} keeps iTunes music libraries in sync, securely backed up and playable from PC/Phone/TV. \vspace{1mm}\\%
    Involved in every aspect from product concept to eventual launch at \href{http://sxsw.com/about/history}{SxSW} and on \href{http://techcrunch.com/2009/03/17/echodio-lets-you-sync-your-itunes-to-the-cloud-300-invites/}{Techcrunch}. Worked mainly on the backend development of the service. \vspace{1mm}\vspace{1mm}\\%   
    \textsl{Skills used: Ruby, Rails, RubyMine, Php, Unit testing and Test Driven Development(TDD), Scrum and Agile Development methods, Bash, Cruise Control, Amazon Web Services(AWS), Rcov, \\competition analysis, Postgres, Domain Specific Language(DSL), Boxee, Flex, Selenium, Subversion, XPath(minor), Flash(minor), Photoshop, AppleScript(minor), JQuery. } \vspace{1mm}\\%

    \textbf{Travel related} \hfill \textbf{October 2007 -- September 2008}\\\vspace{1mm}%
    Travelled to South America, Antarctica for over half this period. During this time, I developed \\ checklottos.com, 4topnews.com and other sites to solve personal annoyances. \vspace{1mm}\\%

    \textbf{Statcounter}, Dublin, Ireland \vspace{2mm}\\\vspace{1mm}%
    \textsl{Contract Work} \hfill \textbf{August 2007 -- September 2007}\\
    Refracting the existing sole developer's codebase  and monitoring for over 9 billion page views a month. 34th busiest website worldwide. \vspace{1mm}\\%
    Dealing with customers on a daily basis and generation of ideas to move the company forward. Recommended that Statcounter enter the ``Europe Young Entrepreneurs Award'' in May which they won.\vspace{1mm}\\%
    \textsl{Skills used: Php, MySql, Multi Lingual Technology, Linux, JavaScript, Subversion, Customer \\ Support, Mobile Development.}\vspace{1mm}\\%


    \textbf{Jeebers}, Dublin, Ireland \vspace{2mm}\\\vspace{1mm}%
    \textsl{Web Developer} \hfill \textbf{February 2006 -- May 2007}\\
    Sole coder on 1timetracking.com. Worked on all areas from early prototype to post launch status from coding to technical and business direction. \\%
    E-commerce solutions for various clients, with full responsibility for bringing each project from \\ concept to post launch status. \vspace{1mm}\\%
    Rapid prototyping of web projects to secure future contracts. \vspace{1mm}\\%
    Worked with Linux on a daily basis, doing shell scripts, SCP backups, etc. Main Linux system \\ displayed ads to customers at garages nationwide, allowing the business to push new advertisements onto each box remotely.\vspace{1mm}\\%
    \textsl{Skills used: Management, Php, MySql, Linux, Ajax, Apache, Fireworks, e-commerce sites, recovering corrupt databases, Subversion, SEO, W3C, JavaScript, benchmarking, Load Balancing, \\Code Optimisation, Documentation, Technical reports.}\vspace{1mm}\\%


    \textbf{DCU School of Computer Applications}, Dublin Ireland \vspace{2mm}\\\vspace{1mm}%
    \textsl{Java Developer} \hfill \textbf{Summer 2005}\\
    Team leader of 4 java developers which delivered on a lecturer's prototype within the prescribed 3 months, to automatically test incoming first years. \vspace{1mm}\\%
    \textbf{DCU School of Computer Applications}, Dublin Ireland \vspace{2mm}\\\vspace{1mm}%
    \textsl{Java Developer} \hfill \textbf{April 2004 - September 2004}\\
    Sole coder on a Php, Java project which was demoed worldwide. Composed of a text to speech system with discussion board functionality required to work on the college's OSS.

    %__________________________________________________________________________________________________________________
    % Operating systems
    \section{\mysidestyle Operating \\Systems}
    Linux(mainly Debian based, ran SUSE/RH as desktop for a year), OS X, Windows.

    %__________________________________________________________________________________________________________________
    % Hobbies
    \section{\mysidestyle Hobbies}
    Travel, history, news.ycombinator.com, storytelling, chess, living life with friends, rugby(captain).

    %___________________
    % Refs
    \section{\mysidestyle Referees} 
    Available on request.

\end{resume}
\end{document}
%______________________________________________________________________________________________________________________
% EOF
